### 2020-11-12 README.Rmd
dropped the usage of word client-replaced it with package

`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).

>>>>

`dataaimsr` is the **AIMS Data Platform R package**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).
